{\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment

### 2020-10-12 documents/charge.tex
lab notebook note
Propagation?

@@

@@

>>>>

As might be expected, the electrostatic properties of the virus differ from that of host cells, both \cite{Icosahedral2019} on the sub-protein level:

\begin{quote}
	Different from insect, plant, and human, viruses had more positively charged than negatively charged segments. In Fig. 1B we show the log (base 10) net-charge frequency value for a selected group of proteins (e.g., Viral proteins) subtracted of the log expected frequency value calculated from the total proteome distribution (i.e., log10-fold-change). Viral proteins were the only class enriched in extremely high positively charged segments (charge ≥ + 17) when compared to the overall proteome (1B-inset with p-values).
\end{quote}

and in the lipid bilayer \cite{Lipid2015} \footnotemark.

\footnotetext{The virus steals its envelope from the host cell; but it tie dyes its duds before it bounces.}

On the largest scale, the net charges of the 11 major proteins coded for by the influenza genome

@@

Other enzymes

@@

\cite{Identification2018}

### 2020-10-12 documents/pseudo_soliton.tex
Propagation?

>>>>

\footnotemark

\footnotetext{Some of the initial work on these precursors (or "forerunners", as they were known at the time) apparently neglected some of the higher-order terms, leading to the conclusion that the signals were "very weak" (Sommerfield). However, the amplitude is often greater than that of the carrier.}

\footnotemark
\footnotetext{Honestly, how cool is this? Like, this unimportant factor (as simple as the rise time!) connects so deeply with Schrodinger's wave-packets - the very same functions that apply for probability distributions - and produces a result so striking - a complete change }

The "asymptotic method", and the fourier series method. Unfortunately, the fourier coefficients and phases provide little intuitive sense for how different input pulses propagate.

%The Somerfield precursor is high-frequency,
